% !TEX root = ../my-thesis.tex
%
\pdfbookmark[0]{Acknowledgement}{Acknowledgement}
\addchap*{Acknowledgement}
\label{sec:acknowledgement}


What a journey!
% 
Four years ago, I have decided to embark on a ship to live a big adventure.
% 
Lacking sailing experience, I still envisioned a voyage in unknown seas, at the crossroads between biology, economics, and applied mathematics.
% 
"\textit{À vaincre sans périls, on triomphe sans joie}" \citep{maufrais1997aventures}, and I purposely wanted to experience storms and dangers.
% 
I have obtained what I expected, and more.
% 
I could only could make it safely back home thanks to the support of the people that have supported me all along this journey. Here are some words that cannot express all the gratitude I have towards them.

I thank my supervisor, Loïc Pellissier, who made this expedition possible by providing the necessary ingredients: a boat and a map. Loïc, thank you for allowing me the freedom to draw the exact route, while kindly indicating me the North when I got lost.
% 
I thank Arnulf Jentzen for guiding me through the strange sea of applied mathematics, besides my lack of mathematical rigor. Arnulf, thank you for your forgiveness and patience, I have come a long way!
% 
I thank Didier Sornette for welcoming ideas with enthousiasm, and give it substance with his experience and knowledge.
% 
I thank Thomas Poulet for his mentorship through ought the voyage. Thomas, you were the one who taught the most important rudiments required to sail! 
% 
I thank Heike Lischke for her help in crucial times.
% 
I thank Sebastian Becker and Pau Vilimelis Aceituno for their goodness, skills and precious hands.
% 

% 
I naturally thank all my friends and colleagues from the Landscape Ecology group. Special thank-you to Giulia Donati and Camille Pitteloud for introducing me to Zürich, and to the world of research. The times when you were here in the lab were the most delightful moments of the voyage.
% 
Special thank-you to Charles de Novaes and Benjamin Flück, who respectively introduced me to Julia and helped me with amazing efficiency when I was about to throw my computer in the bin (which I eventually did).
% 
Special thank-you to Conor Waldock, Marc Grünig and Alexander Skeels for their help and kindness. You guys always had the right advice at the right time!
% 
Special thank-you to Yi Liu who's been, for reasons I still do not understand, constantly harassing me with cheers! 

I am also thankful to all of my wonderful friends, whose company gave me precious half-times to further continue the journey.
% 
Special thank-you to Agathe Trouette, Théo Lafitte, Matthieu Demolin, Yoann Roncajolo, Diego Parlange and Luc Thiebaut for sharing wine, waves and delicious idiocies. "\textit{La connerie, c'est la décontraction de l'intelligence}", this saying by Serge Gainsbourg, has never been so meaningful than with you.
% 
Special thank-you to Simon Ducroz, Valentin Mathieu, Mathieu Duthoit, Baptiste Le Maire, Guillaume Chabert and Alexandre Martineau for sharing moments of pure beauty, friendship and happiness in the high alpine.
% 
Special thank-you to my riding buddies Morgan Guening and Daniel Grogg for introducing me to enduro mountainbiking, and for sharing sheer moments of adrenaline and euphoria. Life in Zürich would have been very different without you guys! 
% 
Special thank-you to my climbing buddies Anita Herger, Eike Köhn and Jonas von Wartburg, for fabulous moments of verticality, bliss and philosophy, and German-climbing sessions.

A massive thank-you to my family for their support. Sabine, Clémentine and Marc, thank you so much for always having been here with me.

I thank again Camille Pitteloud, Marc Grünig, François Rousset, Merin Chacko, Thomas Keggin, Marc Boussange and Sabine Charru for useful comments and feedbacks on earlier versions of this manuscript.

% 
And last but not least, I thank Flora for making every second of this life joyful, with or without perils.
% 
I'll never be as good of a sailor as you are, but we'll become two captains very soon.











% % 
% This adventure would not have been successful / I could not have escaped the pitfals of the PhD without the help of some wonderful people, whom I shall thank.
% % Friends and colleagues
% % Friends
% I thank Giulia and Camille for introducing me to Zürich, and to the world of research. The time where the were in the lab was the most beautiful moments in my PhD.
% % 
% Marc
% % 
% Merin
% % 
% % Colleagues
% I thank Charles for introducing me to the Julia programming language, which I used and developed all along my PhD. 
% % 
% I thank Alex Skeels for always having the right advice as I was getting to the end of the PhD, and his friendliness.
% % 
% I thank Sebastian Becker for introducing me to machine learning, and great programming advices.
% % 
% I thank Benjamin Flück for IT support and his efficiency with any keyboard.
% % 
% % Supervisors
% I thank Heike Lischke for her help.
% % 
% I thank Thomas Poulet for his mentorship informal during all my PhD, and having me encouraged to pursue a PhD after the master thesis.
% % 
% I thank Arnulf Jentzen for giving me his trust and his enthusiasm and interest for the project I proposed him. 
% % 
% I thank Loïc Pellissier for his enthusiasm and open mindedness, and all the freedom he allowed me during the PhD. Giving me the opportunity and freedom to tackle questions, start risky projects. You encouraged me to pursue my (probably too) broad interests and follos random ead I had along the way.
% % Friends
% I thank Morgan for his support and mentoring. I thank the same guy and Daniel for being my riding buddies, with whom I could progress on the trails when I was moving in the reverse direction with the PhD.
% % 
% I thank Jonas for the Tuesday climbing sesh, who allowed me to gain elevation while I was dipping into the valley of shit.
% % 
% % Family
% I thank my parents, and my sister, for supporting me.
% Thanks to my family who I still don’t think know what I do - but that’s ok.
% % 
% And I thank Flora, the love of my life, for making every seconds of my life worth living / less absurd / giving me a direction and lighten my life.
% % 
% We'll hopefully become two captains very soon.

% \textbf{keywords}: gratitude, no words to express, thank you for being there with me. You can first thank a person, and then directely address him something. bring me back to planet earth


\begin{comment}
    some nice phrasing:
    I express my gratitude to xxx
    I am thankful to xxx
\end{comment}