% !TEX root = ../my-thesis.tex
%
\chapter{CV}
\label{sec:CV}

\section*{Personal Information}
% \begin{center}
  \begin{tabular}{l r}
    \textbf{\color{ctcolortitle}Residence} & Zürich, Switzerland\\
    \textbf{\color{ctcolortitle}E-mail}  & \hyperlink{emailto:bvictor@ethz.ch}{{\color{ctcoloraccessory}bvictor@ethz.ch}}\\
    \textbf{\color{ctcolortitle}Website} & \hyperlink{https://vboussange.github.io}{{\color{ctcoloraccessory}vboussange.github.io}}\\
    \textbf{\color{ctcolortitle}Github}  & \hyperlink{https://www.github.com/vboussange}{{\color{ctcoloraccessory}github.com/vboussange}}\\
    \textbf{\color{ctcolortitle}Age}  & Born 1995 (age 27)\\
    \textbf{\color{ctcolortitle}Citizenship}  & France citizen\\
    \end{tabular}
% \end{center}

\section*{Personal skills}
\begin{tabular}{l r}
  \textbf{\color{ctcolortitle}Languages} & English (fluent)\\
            & French (native)\\
            & Spanish (B2) \\
            & German (B1) \\
  \emptySeparator
  \textbf{\color{ctcolortitle}Programming languages} & Julia\\
                        & Python\\
                        & C++\\
                        & Java\\
                        & Matlab\\
                        & R\\
                        & Bash\\
                        & VBA\\

  \textbf{\color{ctcolortitle}Sports} & Ski mountaineering \\
          & Alpinism \\
          & Rock climbing \\
          & Enduro mountainbiking \\
          & Surfing \\
\textbf{\color{ctcolortitle}Alpine CV}  & [\hyperlink{https://vboussange.github.io/pages/alpine_cv/}{{\color{ctcoloraccessory} vboussange.github.io/pages/alpine\_cv/}}]
  \end{tabular}

\section*{Education}
\begin{experiences}
    \experience
      {10.2022}   {Ph.D in Environmental Sciences}{Swiss Federal Institute for Forest, Snow and Landscape (WSL | Swiss Federal Institute of Technology Zurich, ETH)}{Switzerland}
      {09.2018} {\textit{Forward and inverse modelling of eco-evolutionary processes in biological and economic systems}.
                      %   \begin{itemize}
                      %     \item Part I: "\textit{Neutral and adaptive diversification in spatial graphs}"                      
                      %     \item Part II: "\textit{Scientific Machine Learning with applications to eco-evolutionary modeling}"                
                      %     \item Part III: "\textit{Econobiology: understanding economic dynamics with biological models}"   
                      %   \end{itemize}
                      Under the guidance of Prof. Dr. Loïc Pellissier.
                      }
                      {computational biology, mathematical modeling, scientific machine learning, complex systems, complexity economics}
    \emptySeparator
    \experienceshort
      {06.2017} {Full year academic exchange}{University of New South Wales (UNSW Sydney)}{Australia}
      {09.2016} {computational methods for finance, electrical energy, chemical reaction engineering}
      % computational methods for finance, electrical energy, chemical reaction engineering
    \emptySeparator
    \experience
      {06.2017}{Master thesis in theoretical geomechanics}{UNSW Sydney | CSIRO}{Australia}
      {02.2017}{\textit{Numerical continuation and bifurcation analysis for unconventional geomechanics}. Under the guidance of Dr. Thomas Poulet.
                      }
                      {theoretical geomechanics, numerical continuation, bifurcation analysis}
    \emptySeparator
    \experience
    {08.2018}{M.S. in Energy and Environmental Engineering}{Institut National Des Sciences Appliquées de Lyon (INSA Lyon)}{France}
    {09.2013} {Three-year undergraduate engineering course in Energy and Environmental Systems, focused on Advanced Energy Systems and Efficiency.
    }{fluid mechanics, thermodynamics, electrical networks and optimisation, energy markets}
    \emptySeparator
    \experience
    {08.2018}{B.S. in Mathematics and Physics}{Institut National Des Sciences Appliquées de Lyon (INSA Lyon)}{France}
    {09.2013}{Ranking : 21/650 students.}{fluid mechanics, thermodynamics, electrical networks and optimisation, energy markets}
  \end{experiences}

\section*{Professional appointments}
\begin{experiences}
    \experienceshortbis
      {08.2018}{R\&D intern}{Compagnie National du Rh\^one (CNR)}{France}
      {03.2018}{Development of an Energy Management System based on various optimisation techniques for optimal production of renewable resources. Applications to EU sponsored projects: \hyperlink{https://www.jupiter1000.eu/english}{{\color{ctcoloraccessory}Jupiter1000} (power-to-gas)},
      \hyperlink{https://www.cnr.tm.fr/en/innovation/close-to-the-pulse-of-the-territories/}{\color{ctcoloraccessory} Move in pure} (vehicle-to-grid),
      \hyperlink{https://www.youtube.com/watch?v=962bBweyx1s}{{\color{ctcoloraccessory} Marie-Galante island}} (micro-grid)}{}
  \end{experiences}

\section*{Publications}
\subsection*{Peer-reviewed}
\begin{enumerate}[1.]
  \item \textbf{Boussange, V.} \& Pellissier, L., \textit{Eco-evolutionary model on spatial graphs reveals how habitat structure affects phenotypic differentiation}. \hyperlink{https://doi.org/10.1038/s42003-022-03595-3}{\color{ctcoloraccessory} Commun Biol} 5, 668 (2022). \hyperlink{https://www.biorxiv.org/content/10.1101/2021.07.06.451404.abstract}{[{\color{ctcoloraccessory}bioRxiv}]}
\end{enumerate}
\subsection*{Preprints}
\begin{enumerate}[1.]
  \item \textbf{Boussange, V.}, Vilimelis-Aceituno, P., Pellissier, L., \textit{Mini-batching ecological data to improve ecosystem models with machine learning} \hyperlink{https://www.biorxiv.org/content/10.1101/2022.07.25.501365v1}{[{\color{ctcoloraccessory}bioRxiv}]} (2022), 46 pages. In review.
  \item \textbf{Boussange, V.}, Becker, S., Jentzen, A., Kuckuck, B., Pellissier, L., \textit{Deep learning approximations for non-local nonlinear PDEs with Neumann boundary conditions}. \hyperlink{https://arxiv.org/abs/2205.03672}{[{\color{ctcoloraccessory}arXiv}]} (2022), 59 pages. Revision requested from Partial Differential Equations and Applications.
\end{enumerate}
\subsection*{Proceedings}

\begin{enumerate}[1.]
  \item Poulet, T., Alevizos, S., Veveakis, M., \textbf{Boussange, V.}, Regenauer-Lieb, K., \textit{Episodic mineralising fluid injection through chemical shear zones}, \hyperlink{https://www.biorxiv.org/content/10.1101/2021.07.06.451404.abstract}{ASEG Extended Abstracts} (2018), 5 pages.
\end{enumerate}

\subsection*{In preparation}
\begin{enumerate}[1.]
  \item \textbf{Boussange, V.}, Sornette, D., Lischke, H., Pellissier, L., \textit{Analogous forces to ecological interactions, dispersal and mutations shape the dynamics of economic activities}.
\end{enumerate}


\section*{Talks}
\begin{scholarship}
  \scholarshipentry{07.2022}{Speaker}{\textsc{HighDimPDE.jl}: A Julia package for solving high-dimensional PDEs, JuliaCon2022, online.  \hyperlink{https://www.youtube.com/watch?v=4sXqGhhknT4}{\color{ctcoloraccessory}youtube.com/watch?v=4sXqGhhknT4}}
  \scholarshipentry{06.2022}{Speaker}{Interpretable machine learning for forecasting dynamical processes in ecosystems, World Biodiversity Forum, Davos, Switzerland.}
  \scholarshipentry{06.2022}{Invited speaker}{Investigating empirical patterns of biodiversity with mechanistic eco-evolutionary models, Seminar at the Theoretical Ecology and Evolution group, Universität Bern.}
  \scholarshipentry{11.2021}{Invited speaker}{Numerical approximations of solutions of highly dimensional, non-local nonlinear PDEs, StAMBio seminar, St Andrews, UK.}
  \scholarshipentry{10.2021}{Speaker}{Graph topology and habitat assortativity drive phenotypic differentiation in an eco-evolutionary model, Conference on Complex Systems, Lyon, France.}
  \scholarshipentry{10.2021}{Speaker}{Using graph-based metrics to assess the effect of landscape topography on diversification, ECBC, Amsterdam, Netherlands.}
  \scholarshipentry{09.2021}{Speaker}{Solving non-local nonlinear Partial Differential Equations in high dimensions with HighDimPDE.jl, International Conference on Computational Methods in Systems Biology, Bordeaux, France.}
  \scholarshipentry{04.2021}{Speaker}{Responses of neutral and adaptive diversity to complex geographic population structure, Mathematical Population Dynamics, Ecology and Evolution, CIRM Marseille, France.}
\end{scholarship}

\section*{Softwares}

\begin{projects}
	\project
	{MiniBatchInference.jl}{2022}
	{\github{vboussange/MiniBatchInference.jl}}
	{A Julia package for maximum likelihood estimation and model selection of strongly nonlinear dynamical models.}
	{Julia}
  \emptySeparator
	\project
	{HighDimPDE.jl}{2021}
	{\github{vboussange/HighDimPDE.jl} }
	{A Julia package that breaks down the curse of dimensionality in solving non local, non linear PDEs.}
	{Julia}
  \emptySeparator		
	\projectmy
	{EvoId.jl}{2019}{2021}
	{\github{vboussange/EvoId.jl} }
	{Evolutionary individual based modelling, mathematically grounded.}
	{Julia}
  \emptySeparator
  \project
	{OptiVPP}{2018}
	{\website{}{confidential}}
	{Energy Management System for Virtual Power Plants.}
	{Python, GAMS}
\end{projects}

\subsection*{Open source software contributions}
\begin{tabular}{l}
SciML\\
DiffEqFlux.jl\\ 
CUDA.jl\\ 
Flux.jl\\ 
LightGraphs.jl
\end{tabular}

\section*{Teaching and supervision}
\begin{experiences}
  \experienceshort
    {12.2020}{701-3001-00L Environmental Systems Data Science}{ETH Zürich, D-USYS}{Switzerland}
    {09.2020}
    {Undergraduate course. In charge of the unit \textit{Supervised Deep Learning - Application}.}
    \emptySeparator
  \experienceshort
    {06.2020}{262-0100-00L Lab rotation}{ETH Zürich, D-BSSE}{Switzerland}
    {04.2020}
    {Supervision of Cecilia Valenzuela Agui in the frame of her MS in \textit{Computational Biology and Bioinformatics}: \textit{How Climatic Conditions shape Biodiveristy Patterns?}}
    \emptySeparator
  \experienceshort
    {12.2020}{Taste of research internship}{Polytech Nice-Sophia}{France}
    {09.2020}
    {Supervision of Nicolas Demolin for his research internship in the frame of his MS in \textit{Applied Mathematics and Modeling}: \textit{Dynamical modelling of the Product Space.}}
\end{experiences}

\section*{Reviews}
\begin{experiences}
  \experienceveryshort{2022}{Journal of Open Source Software}
  \experienceveryshort{2019}{Journal of Theoretical Biology}
\end{experiences}
