% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Scholarships and additional info
\sectionTitle{Talks}{\faRss}

\begin{scholarship}
    \scholarshipentry{July 2022}{Speaker, \textit{\textbf{HighDimPDE.jl}: A Julia package for solving high-dimensional PDEs}, JuliaCon2022, online.  \hyperlink{https://www.youtube.com/watch?v=4sXqGhhknT4}{[video]}}
    \scholarshipentry{June 2022}{Speaker, \textit{Interpretable machine learning for forecasting dynamical processes in ecosystems}, World Biodiversity Forum, Davos, Switzerland.}
    \scholarshipentry{June 2022}{Invited speaker, \textit{Investigating empirical patterns of biodiversity with mechanistic eco-evolutionary models}, Seminar at the Theoretical Ecology and Evolution group, Universität Bern.}
    \scholarshipentry{November 2021}{Invited speaker, \textit{Numerical approximations of solutions of highly dimensional, non-local nonlinear PDEs}, StAMBio seminar, St Andrews, UK.}
	\scholarshipentry{October 2021}{Speaker, \textit{Graph topology and habitat assortativity drive phenotypic differentiation in an eco-evolutionary model}, Conference on Complex Systems, Lyon, France.}
	\scholarshipentry{October 2021}{Speaker, \textit{Using graph-based metrics to assess the effect of landscape topography on diversification}, ECBC, Amsterdam, Netherlands.}
	\scholarshipentry{September 2021}{Speaker, \textit{Solving non-local nonlinear Partial Differential Equations in high dimensions with HighDimPDE.jl}, International Conference on Computational Methods in Systems Biology, Bordeaux, France.}
	\scholarshipentry{April 2021}{Speaker, \textit{Responses of neutral and adaptive diversity to complex geographic population structure}, Mathematical Population Dynamics, Ecology and Evolution, CIRM Marseille, France.}
\end{scholarship}