% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Education}{\faUniversity}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {October 2022 \hfill (expected)}   {Ph.D in Environmental Sciences}{Swiss Federal Institute for Forest, Snow and Landscape (WSL | Swiss Federal Institute of Technology Zurich, ETH)}{Switzerland}
    {September 2018} {"\textit{Forward and inverse modelling of eco-evolutionary processes}".
                    %   \begin{itemize}
                    %     \item Part I: "\textit{Neutral and adaptive diversification in spatial graphs}"                      
                    %     \item Part II: "\textit{Scientific Machine Learning with applications to eco-evolutionary modeling}"                
                    %     \item Part III: "\textit{Econobiology: understanding economic dynamics with biological models}"   
                    %   \end{itemize}
                    Under the guidance of Prof. Dr. Loïc Pellissier.
                    }
                    {computational biology, mathematical modeling, scientific machine learning, complex systems, complexity economics}
  \emptySeparator
  \experience
    {June 2017} {Full year academic exchange}{University of New South Wales (UNSW Sydney)}{Australia}
    {September 2016} {}{computational methods for finance, electrical energy, chemical reaction engineering}
    % computational methods for finance, electrical energy, chemical reaction engineering
  \emptySeparator
  \experience
    {June 2017}{Master thesis in theoretical geomechanics}{UNSW Sydney | CSIRO}{Australia}
    {February 2017}    {"\textit{Numerical continuation and bifurcation analysis for unconventional geomechanics}". Under the guidance of Dr. Thomas Poulet.
                    }
                    {theoretical geomechanics, numerical continuation, bifurcation analysis}
  \emptySeparator
  \experience
  {August 2018}       {B.S./ M.S. in Energy and Environmental Engineering}{Institut National Des Sciences Appliquées de Lyon (INSA Lyon)}{France}
  {September 2013} {
  \begin{itemize}
      \item Two-year undergraduate intensive course in mathematics and physics.
Ranking : 21/650 students.
      \item Three-year undergraduate engineering course in Energy and Environmental Systems, focused on Advanced Energy Systems and Efficiency.
  \end{itemize}
  }{fluid mechanics, thermodynamics, electrical networks and optimisation, energy markets}
\end{experiences}
